Social Conditions of Fear

### 2023-11-28 scripts/manuscript.qmd

@@

@@

summary(complete(complete5, 1))

>>>>

#XM: I understand this is a draft version and would suggest adding more information about the data set.

@@

    #XM: To me this question really doesn't make sense... there are transgender males and females, did they mean non-binary? I'd feel concerned about this variable

@@

#XM: there are still NAs in the imputated data even after I tried changing parameters in mice(), maybe reducing the variables would help? also I think it might be helpful to investigate missing patterns and correlations before imputations
summary(complete(complete5, 1))
